---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

## nadp

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active) [![Travis-CI Build Status](https://travis-ci.org/jsta/nadp.svg?branch=master)](https://travis-ci.org/jsta/nadp) 

This package is an R interface to faciliate access to the National Atmospheric Deposition Program map data.
 
## Installation

```{r eval=FALSE}
# install devtools if not found
# install.packages(devtools)
devtools::install_github("jsta/nadp")
```

## Usage

```{r }
library(nadp)
library(raster)
```

### Download external data and store in file system

```{r message=FALSE, eval=FALSE}
nadp_get(years = 2010, products = "totalN")
```

### List files

```{r eval=FALSE}
nadp_ls()
```

### Load data

```{r }
dt <- nadp_load(years = 2010, products = "totalN")
names(dt)
class(dt)
plot(dt); title("2010 totalN deposition")
```

## Contributing

Contributions welcome in the form of issues and pull requests.

## Prior Art

This package uses the `externalrdata` [package template](https://github.com/jsta/externalrdata)
